A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-22 bioc-workflow.Rmd
point size and thresholding

>>>>

The adjustment of the point size intuitively confers important
information that is more difficult to defined formally, but that we
will address in the next section. The classifier (SVM in our case, but
this is also valid of other classifiers) defines boundaries based on
the labelled marker proteins. These class/organelle boundaries define
how non-assigned proteins are classifier and with what confidence.
